High-Velocity Outflows Without AGN Feedback: \\ Eddington-Limited Star Formation in Compact Massive Galaxies

### 2012-05-08 tex/sigmasfr/ms.tex
pre submission version

\documentclass[apj]{emulateapj}
%\documentclass[12pt,preprint]{aastex}

\newcommand{\kms}{km~s$^{-1}$}
\newcommand{\mgii}{\textrm{Mg}~\textsc{ii}}
\newcommand{\nev}{[\textrm{Ne}~\textsc{v}]}
\newcommand{\oii}{[\textrm{O}~\textsc{ii}]}
\newcommand{\oiii}{[\textrm{O}~\textsc{iii}]}
\newcommand{\msun}{M$_{\odot}$}
\newcommand{\mstar}{M$_{*}$}
\newcommand{\units}{M$_{\odot}$~yr$^{-1}$~kpc$^{-2}$}
\newcommand{\lrest}{\lambda_{\textnormal{\scriptsize{rest}}}}
\newcommand{\lobs}{\lambda_{\textnormal{\scriptsize{obs}}}}
\newcommand{\sigmasfr}{\Sigma_{\textnormal{\scriptsize{SFR}}}}
\newcommand {\apgt} {\ {\raise-.5ex\hbox{$\buildrel>\over\sim$}}\ }
\newcommand {\aplt} {\ {\raise-.5ex\hbox{$\buildrel<\over\sim$}}\ }

\shorttitle{Compact Starbursts Revealed by HST and WISE}
\shortauthors{Diamond-Stanic et al.}

@@

%\title{HST and WISE Reveal Compact Starbursts Driving 1000
%  \kms\ Outflows}

\title{In the Crucible: Massive Compact Galaxies with High-Velocity
  Outflows and Eddington-Limited Star Formation}

\author{Aleksandar M. Diamond-Stanic\altaffilmark{1,2}, John
  Moustakas\altaffilmark{1}, Christy A. Tremonti\altaffilmark{3},
  Alison L. Coil\altaffilmark{1}, Ryan C. Hickox\altaffilmark{4}, Aday
  Robaina\altaffilmark{5}, Gregory H. Rudnick\altaffilmark{6}, \& Paul
  Sell\altaffilmark{3} }

@@

Based on infrared photometry from the Wide-field Infrared Survey
Explorer (WISE) and optical morphologies from the Hubble Space
Telescope (HST), we present the discovery of compact, obscured star
formation in galaxies that exhibit $1000$~\kms\ outflows.  The implied
star formation rate (SFR) surface densities approach
$\sigmasfr=5000$~\msun~yr$^{-1}$~kpc$^{-2}$, and we argue that
feedback associated with this starburst event is a likely mechanism
for launching the high-velocity outflows.

@@

The central regions of elliptical galaxies are thought to form in
compact starbursts \citep[e.g.,][]{kor09,hop09}.  Feedback associated
with such starbursts can produce outflows driven by thermal energy
from supernova explosions \citep[e.g.,][]{che85}, stellar winds
\citep[e.g.,][]{lei92}, and momentum input from both supernova ram
pressure and radiation pressure on dust grains \citep[e.g.,][]{mur05}.
It has been argued that such feedback imposes a limit on the maximum
star-formation rate surface density ($\sigmasfr$) for starbursts
\citep[e.g.,][]{leh96,meu97,mur05,tho05} and the maximum stellar
surface density for elliptical galaxies and star clusters
\citep[e.g.,][]{hop10}.

% The relative importance of momentum injection versus thermal heating
% may vary as a function of galaxy mass \citep[e.g.,][]{hop12}, with
% thermal heating being less efficient in galaxies with larger gas
% densities and shorter cooling times.  Massive star clusters with large
% gas surface densities are a potential launching point for
% galactic-scale outflows driven by radiation pressure
% \citep[e.g.,][]{mur11}.

Galactic winds are ubiquitous in star-forming galaxies at all
redshifts and generally exhibit outflow velocities in the
100--500~\kms\ range
\citep[e.g.,][]{hec00,sha03,mar05,rup05,wei09,rub10,ste10}.  Thus, the
discovery of $|v|>1000$~\kms\ outflows in a sample of massive
($\textnormal{\mstar}\approx10^{11}$~\msun) post-starburst galaxies at
$z\sim0.6$ by \citet{tre07} suggested that a more energetic source,
such as feedback from an accreting supermassive black hole
\citep[e.g.,][]{sil98,dim05,deb12}, could have been responsible for
launching the winds.

However, it also plausible that feedback from a compact starburst
could expel gas with such large velocities.  Indeed, there is evidence
for a positive correlation between outflow velocity and starburst
luminosity \citep[e.g.,][]{mar05,rup05,tre07}, albeit with significant
scatter.  Furthermore, \citet{hec11} recently found outflows with
maximum velocities reaching $-1500$~\kms\ in a sample of local
starbursts with compact nuclei, and argued that such velocities could
be explained by feedback from massive stars.

% $|v|\gtrsim1000$~\kms\

In this Letter, we present results for a sample of massive galaxies at
$z\sim0.6$ that exhibit $|v|\apgt1000$~\kms\ outflows, expanding on
the sample from \citet{tre07}.  We seek to test whether the energetic
outflows in these galaxies could have been driven by feedback from
starbursts with very large star-formation rate (SFR) surface densities
($\sigmasfr$).  Our analysis combines galaxy sizes obtained with the
Hubble Space Telescope (HST) with star-formation rates and stellar
masses estimated from WISE, Spitzer, SDSS, and GALEX photometry.

% For example, there is evidence for a positive correlation between
% outflow velocity and starburst luminosity \citep[e.g.,][]{mar05},
% albeit with significant scatter.  Furthermore, \citet{hec11} recently
% found outflows reaching velocities of $-1500$~\kms\ in a sample of
% local starbursts with compact nuclei, and argued their higher
% velocities could be explained by feedback exerted by a large number of
% massive stars that are confined to a small radius.

% [which has been invoked theoretically as
%  a mechanism to quench star formation in galaxies,

% Winds are also common in active galactic nuclei (AGNs) with velocities
% in the 1000--20,000~\kms range \citep[e.g., ][]{cre03}, although it is
% unclear whether AGN feedback plays an important role in regulating
% star formation in galaxies.  There is clear observational evidence
% that active galactic nuclei (AGNs) produce outflows
% \citep[e.g.,][]{cre03} and that the outflowing gas can extend to
% $>$kpc scales \citep[e.g.,][]{rup11}, it is unclear whether such
% feedback plays an important role globally in quenching star formation.

% Feedback from massive stars and active black holes has important
% implications for galaxy evolution (e.g., luminosity function, star
% formation, galaxy color bi-modality, mass-metallicity relation,
% enrichment of IGM).

% Feedback from accreting supermassive black holes has also been invoked
% theoretically as a mechanism for quenching star formation in galaxies
% \citep[e.g.,][]{sil98,gra04,dim05}.  There is clear observational
% evidence that active galactic nuclei (AGNs) produce outflows
% \citep[e.g.,][]{cre03} and that the outflowing gas can extend to
% $>$kpc scales \citep[e.g.,][]{rup11}, but it is unclear whether such
% feedback plays an important role globally in quenching star formation
% and shaping the galaxy mass function.

% and optical spectra ($\lrest=2500$-5200~\AA)

%  The spectral region surrounding the
%  \mgii~$\lambda\lambda2796,2803$ absorption alines, which are used to
%  measure outflow velocities, is highlighted in both wavelength and
%  velocity space.

%  and are scaled to match the WISE channel 2 photometry ($\lobs=4.6$~$\mu$m)
% (\mgii~$\lambda2796$ is plotted in blue and \mgii~$\lambda2803$ is plotted in red)

@@

\subsection{HST/WFC3 Imaging}

Our sample derives from 29 galaxies targeted for HST/WFC3 imaging in
programs 12019 and 12272 (PI: C. Tremonti).  Using the F814W filter on
the UVIS channel, which has $0.04\arcsec$ pixels and
$\textnormal{FWHM}=0.074\arcsec$, we obtained $4\times10$~min
exposures in a single orbit for each galaxy.  The dithered images were
processed with
MultiDrizzle\footnote{http://stsdas.stsci.edu/multidrizzle/} to
produce science mosaics with $0.02\arcsec$ pixels.  For each galaxy,
we use GALFIT \citep{pen02,pen10} to model the two-dimensional surface
brightness profile with a single Sersic component, using stars in the
images to construct the model point-spread function (PSF).  The Sersic
index (n) and effective radius ($r_e$) are free parameters in the
model.  In cases where the best-fit model returns $n>4$, we also fit
an $n=4$ de Vaucouleurs model \citep{dev48}, yielding a larger $r_e$
value (due to the covariance between $n$ and $r_e$), and we use these
these larger effective radii in our analysis.

For this paper, we are most interested in the galaxies with the
largest $\sigmasfr$ values, which also have the smallest effective
radii.  We show the HST images for three high-$\sigmasfr$ galaxies in
Figure~\ref{fig:seds}.  In all three cases, the single-component model
GALFIT accounts for $>85\%$ of the total flux.  The residuals show
diffuse emission that is consistent with these systems being
late-stage galaxy mergers after final coalescence, although we defer a
detailed comparison of the observed morphologies with expectations
from merger simulations to future work.

For the most compact galaxy (J0905+5759, $r_e=0.013\arcsec$ or
100~pc), we also show the observed one-dimensional surface brightness
profile in the bottom-right panel of Figure~\ref{fig:profile}.  We
compare to the profiles of six stars in the same image, the best-fit
de Vaucouleurs model, and a de Vaucoulerus model with a larger
effective radius ($r_e=0.04\arcsec$, the native WFC3/UVIS pixel size,
which corresponds to a physical scale of 290~pc).  This comparison
illustrates that this galaxy, while only marginally resolved with an
effective radius that is $\sim20\%$ of the image FWHM, is clearly more
extended than a point source.

For such a compact source, there is significant uncertainty in our
$r_e$ measurement given uncertainties in the model PSF.  To quantify
this uncertainty, we used TinyTim to generate a model PSF that is
artificially narrower than the stars in the image (convolving the
output of tiny2 with a $\textnormal{FWHM}=0.04\arcsec$ Gaussian,
whereas the image FWHM is $0.074\arcsec$) and found that this
increased the effective radius in the GALFIT model by a factor of two.
We also fit a two-component PSF+Sersic model, but found that the
Sersic component dominates the fit, yielding a similar effective
radius.  Furthermore, the spectrum of the galaxy shows no evidence for
an AGN contribution to the $I$-band continuum (see
Figure~\ref{fig:spectra}), so there is no clear motivation for
including an unresolved, point-source component in the model.  We
conclude that this galaxy is quite compact and that our $r_e$ estimate
of 100~pc, while uncertain, is likely accurate within a factor of two.

\begin{figure}[!t]
%\includegraphics[angle=90,scale=0.68]{sigmasfr_datafigure.ps}
\includegraphics[angle=0,scale=0.41]{3seds.ps}
\caption{Left: Observed UV--IR SEDs ($\lrest=0.1$--15~$\mu$m) for
  three galaxies with large SFR surface densities
  ($\sigmasfr>3000$~\units).  We show stellar population fits to the
  $\lrest=0.1$--3~$\mu$m emission (black solid line) and three
  templates for dust emission \citep[M82 starburst, Arp 220 starburst,
    and obscured quasar;][]{pol07}.  The starburst templates provide
  reasonable fits to the $\lobs=12$ and 22~$\mu$m WISE photometry,
  while the quasar template does not.  Right: HST/WFC3 F814W images
  (probing $\lrest\approx5000$~\AA) showing that these galaxies are
  dominated by a compact nucleus.}
\label{fig:seds}
\end{figure}
% scaled to the WISE $\lobs=4.6~\mu$m flux.

\begin{figure}[!t]
\includegraphics[angle=0,scale=0.41]{profile.ps}
\label{fig:profile}
\caption{One-dimensional surface brightness profile for J0905+5759,
  which has the smallest effective radius in the sample.  The observed
  profile is shown as the solid black line, and the profiles of six
  stars in the same image are shown in blue.  The best-fit de
  Vaucouleurs profile with $r_e=100$~pc is shown as a dashed red line,
  and for comparison a broader profile with $r_e=0.04\arcsec=290$~pc
  is shown as the dotted green line.  This galaxy is quite compact,
  but is more extended than a point source.}
\end{figure}

\subsection{Photometry, Stellar Masses, and Star-formation rates}

We gathered photometry from the All-Sky Release of the Wide-field
Infrared Survey Explorer \citep[WISE,][]{wri10}, the Seventh Data
Release of the Sloan Digital Sky Survey \citep[SDSS,][]{aba09}, and
General Release 6 from the Galaxy Evolution Explorer (GALEX).  We also
obtained $5\times30$~sec dithered exposures in the 3.6~$\mu$m and
4.5~$\mu$m for all sources with the Infrared Array Camera
\citep{faz04} on the Spitzer Space Telescope \citep{wer04} as part of
General Observer program 60145 (PI: C. Tremonti).  We used the
post--basic calibrated data to perform aperture photometry on all
sources, and we also used the
APEX\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/dataanalysistools/tools/mopex/}
point-source extraction software for photometry of sources in crowded
fields.  All the photometry was corrected for Galactic extinction
based on the \citet{sch98} dust maps.  We show spectral energy
distributions (SEDs) for the three high-$\sigmasfr$ galaxies in
Figure~\ref{fig:seds}.

We estimate IR-based star-formation rates for the 25/29 galaxies with
WISE 12~$\mu$m detections by fitting \citet{cha01} templates to their
12 and 22~$\mu$m fluxes.  For the 14/29 galaxies with 22~$\mu$m
detections, the method of \citet{ruj12} yields SFRs that agree with
the above values within 0.05~dex.  We note that the shape of the IR
SED for star-forming galaxies depends on the surface density of star
formation \citep[e.g.,][]{ruj11,elb11}, with more compact starbursts
having larger total-IR (8--1000~$\mu$m) to mid-IR (8--24~$\mu$m)
ratios.  The extreme $\sigmasfr$ values of our sample imply large
total-IR to mid-IR ratios, characteristic of the most luminous
galaxies in the local universe \citep[e.g.,][]{cha01,dal02,rie09}.
For the 8/29 sources where we estimate $SFR_{IR}>200$~\msun~yr$^{-1}$
above, using the most luminous local templates would yield SFRs that
are larger by 0.5~dex.

We also estimate star-formation rates and stellar masses based on
stellar population fits to the $\lrest=0.1$--3~$\mu$m SEDs using the
method of \citet{mou11}.  For galaxies with
$SFR_{IR}>50$~\msun~yr$^{-1}$, there is agreement between these
UV-optical-based estimates and $SFR_{IR}$ with a scatter of 0.32~dex.

\begin{figure}[!t]
\includegraphics[angle=0,scale=0.41]{spectra.ps}
\caption{Spectra covering $\lrest=2500$--5200~\AA\ for the three
  galaxies shown in Figure~\ref{fig:seds}.  These spectra are
  dominated by light from the young stellar population and exhibit
  \oii~$\lambda3727$, H$\beta$~$\lambda4861$, and \oiii~$\lambda5007$
  emission lines.  The panels on the right zoom on the
  \mgii~$\lambda\lambda2796,2803$ spectral region in both wavelength
  and velocity space.  The spectrum in the bottom panel has sufficient
  spectral resolution ($\textnormal{FWHM}\approx8$~\kms) to resolve
  the intrinsic shape of the absorption-line profile, revealing that
  the gas near the centroid velocity has unity covering factor.}
\label{fig:spectra}
\end{figure}

\begin{figure*}[!t]
\begin{center}
\includegraphics[angle=0,scale=.8]{sigmasfr.ps} %\\
%\includegraphics[angle=0,scale=.7]{sizemass_sigmasfr.ps}
%\caption{$\sigmasfr$--mass and size--mass relationships.}
\caption{SFR surface densities and stellar masses for the HST--WISE
  sample described in this paper (black circles, with symbol size
  proportional to outflow velocity), along with samples of gas-rich
  mergers (orange squares) and star-forming galaxies (shown with 68\%
  contours).  We mark the empirical threshold for launching winds
  \citep[dotted line, $\sigmasfr=0.1$~\units;][]{hec02}, the
  90th-percentile starburst intensity limit from \citet{meu97} (dashed
  line, $\sigmasfr=45$~\units), and the Eddington limit from radiation
  pressure on dust grains \citep[solid line,
    $\sigmasfr\approx2000$~\units;][]{mur05,tho05,hop10}.  Our
  HST--WISE sample overlaps with the region characterized by gas-rich
  mergers, and extends to very large SFR surface densities near the
  Eddington limit.  The sample of gas-rich mergers includes ULIRGs
  \citep{vei06}, Lyman break analogs with dominant central objects
  \citep{ove09}, and the local compact starburst Arp 220 \citep{sco97,
    ken98, rod08}.  The samples of star-forming galaxies are drawn
  from \citet{wuy11} at $0.02<z<0.2$ (solid black contour),
  $0.5<z<1.5$ (dashed red countour), and $1.5<z<2.5$ (dotted purple
  contour), and from \citet{law12} at $2.5<z<3.6$ (dash-dotted blue
  contour). }
\label{fig:sigmasfr}
\end{center}
\end{figure*}

\subsection{Optical Spectroscopy}

We present low-resolution $R=1000-3000$ spectroscopy from MMT/Blue
Channel and SDSS (J1506+5402), Magellan/MagE (J1341-0321), and
Keck/LRIS (J0905+5759) in Figure~\ref{fig:spectra.}.  We also
highlight the \mgii~$\lambda\lambda2796,2803$ absorption lines, which
are used use to measure outflow velocities.

For J0905+5759 we show the \mgii\ absorption-line profiles from
$R\approx37,000$ spectra obtained with Keck/HIRES.  The oscillator
strength of \mgii~$\lambda$2796 is twice that of \mgii~$\lambda$2803,
but the equivalent widths of the two lines and the shapes of the line
profiles are quite similar, indicating that both lines are optically
thick.  The fact that the absorption line profile approaches zero near
the velocity centroid $v=-2470$~\kms\ indicates that the outflowing
gas covers the entire continuum source at these velocities.

%\section{Analysis}
%
%\subsection{Star-formation Rates and Stellar Masses}
%
%\subsection{Morphologies and Sizes}
%
%\subsection{Outflow Kinematics and Covering Factors}

% \begin{figure*}[!t]
% \begin{center}
% \includegraphics[angle=0,scale=.8]{sizemass_sigmasfr.ps}
% \caption{size--mass relationship.}
% \label{fig:sizemass}
% \end{center}
% \end{figure*}

>>>>

\documentclass[apj]{emulateapj}

\newcommand{\kms}{km~s$^{-1}$}
\newcommand{\mgii}{\textrm{Mg}~\textsc{ii}}
\newcommand{\nev}{[\textrm{Ne}~\textsc{v}]}
\newcommand{\oii}{[\textrm{O}~\textsc{ii}]}
\newcommand{\hii}{\textrm{H}~\textsc{ii}}
\newcommand{\oiii}{[\textrm{O}~\textsc{iii}]}
\newcommand{\msun}{M$_{\odot}$}
\newcommand{\mstar}{M$_{*}$}
\newcommand{\units}{M$_{\odot}$~yr$^{-1}$~kpc$^{-2}$}
\newcommand{\lrest}{\lambda_{\textnormal{\scriptsize{rest}}}}
\newcommand{\lobs}{\lambda_{\textnormal{\scriptsize{obs}}}}
\newcommand{\sigmasfr}{\Sigma_{\textnormal{\scriptsize{SFR}}}}
\newcommand{\sfrir}{\textnormal{SFR}_{\textnormal{\scriptsize{IR}}}}

\shorttitle{Compact Starbursts Driving High-Velocity Outflows}
\shortauthors{Diamond-Stanic et al.}

@@

\title{High-Velocity Outflows Without AGN Feedback:
  \\ Eddington-Limited Star Formation in Compact Massive Galaxies}

\author{Aleksandar M. Diamond-Stanic\altaffilmark{1,2}, John
  Moustakas\altaffilmark{1}, Christy A. Tremonti\altaffilmark{3},
  Alison L. Coil\altaffilmark{1}, Ryan C. Hickox\altaffilmark{4}, Aday
  R. Robaina\altaffilmark{5}, Gregory H. Rudnick\altaffilmark{6}, \&
  Paul H. Sell\altaffilmark{3} }

@@

We present the discovery of compact, obscured star formation in
galaxies at $z\sim0.6$ that exhibit $\gtrsim1000$~\kms\ outflows.
Using optical morphologies from the Hubble Space Telescope and
infrared photometry from the Wide-field Infrared Survey Explorer, we
estimate star formation rate (SFR) surface densities that approach
$\sigmasfr\approx3000$~\units, comparable to the Eddington limit from
radiation pressure on dust grains.  We argue that feedback associated
with a compact starburst in the form of radiation pressure from
massive stars and ram pressure from supernovae and stellar winds is
sufficient to produce the high-velocity outflows we observe, without
the need to invoke feedback from an active galactic nucleus.

@@

The central regions of elliptical galaxies are thought to form in
compact starbursts \citep{kor09,hop09}.  Feedback associated with such
starbursts can produce outflows driven by thermal energy from
supernova explosions \citep{che85}, stellar winds \citep{lei92}, and
momentum input from both supernova ram pressure and radiation pressure
on dust grains \citep{mur05}.  It has been argued that such feedback
imposes a limit on the maximum star-formation rate (SFR) surface
density ($\sigmasfr$) for starbursts \citep{leh96,meu97,mur05,tho05}
and the maximum stellar surface density for elliptical galaxies and
star clusters \citep{hop10}.

Galactic winds are ubiquitous in star-forming galaxies at all
redshifts and generally exhibit outflow velocities in the
100--500~\kms\ range, which can be attributed to the stellar processes
described above \citep{hec00,sha03,mar05,rup05,wei09,rub10}.  Outflows
with significantly higher velocities ($|v|>1000$~\kms) were discovered
by \citet{tre07} in a sample of massive
($\textnormal{\mstar}\approx10^{11}$~\msun) post-starburst galaxies at
$z\sim0.6$, and it was suggested that a more energetic source such as
feedback from an accreting supermassive black hole \citep{sil98,dim05}
may be responsible for launching the winds \citep[see][for a recent
  review]{fab12}.

However, it also plausible that feedback from a compact starburst
could expel gas with such large velocities.  Indeed, there is evidence
for a positive correlation between outflow velocity and starburst
luminosity \citep{mar05,rup05,tre07}, albeit with significant scatter.
Furthermore, \citet{hec11} recently found outflows with maximum
velocities reaching $1500$~\kms\ in a sample of local starbursts with
compact nuclei, and argued that such velocities could be explained by
a wind that is launched from $r_0\sim100$~pc and driven by feedback
from massive stars and supernovae.

In this Letter, we measure sizes and SFRs for a sample of massive
galaxies at $z\sim0.6$ that exhibit $\gtrsim1000$~\kms\ outflows,
expanding on the initial study by \citet{tre07}.  We seek to test
whether the energetic outflows in these galaxies could have been
driven by feedback from starbursts with very large SFR surface
densities.  Our analysis combines galaxy sizes measured with the
Hubble Space Telescope (HST) with SFRs and stellar masses estimated
from Wide-field Infrared Survey Explorer (WISE), Spitzer Space
Telescope, Sloan Digital Sky Survey (SDSS), and Galaxy Evolution
Explorer (GALEX) photometry.

% we focus our analysis on the galaxies with the most extreme
% $\sigmasfr$ values.

\begin{figure}[!t]
\includegraphics[angle=0,scale=0.41]{f1.ps}
\caption{Left: Observed UV--IR SEDs ($\lrest=0.1$--15~$\mu$m) for
  three galaxies with the largest SFR surface densities
  ($\sigmasfr\approx3000$~\units).  The top two SEDs are offset by 5
  and 10 magnitudes, respectively.  We show stellar population fits to
  the $\lrest=0.1$--3~$\mu$m emission (black solid line) and three
  templates for dust emission \citep[M82 starburst, blue dashed line;
    Arp 220 starburst, green dot-dashed line; obscured quasar, red
    dotted line;][]{pol07} scaled to match the $\lobs=4.6~\mu$m band.
  The starburst templates provide reasonable fits to the $\lobs=12$
  and 22~$\mu$m WISE photometry, while the quasar template does not.
  Right: HST/WFC3 F814W images (probing $\lrest\approx5000$~\AA)
  showing that these galaxies are dominated by a compact nucleus.}
\label{fig:seds}
\end{figure}

@@

\subsection{Morphologies and Sizes}

We observed 29 galaxies with HST (programs 12019 and 12272) selected
from a parent sample of $\sim10^3$ galaxies at $0.35<z<1.0$ with
post-starburst spectral features: B or A-star dominated stellar
continua and moderately weak nebular emission
($\textnormal{EW}(\oii)<20$~\AA; see C. Tremonti, et al., in
preparation for more details).  The galaxies targeted with HST were
those with the youngest derived post-burst ages
$t_{burst}\lesssim300$~Myr.  Thus, by design, this sample has bluer
$U-B$ colors and stronger emission lines than typical post-starburst
samples \citep{coi11}.  Our subsequent UV--IR SED analysis (see
Section~\ref{sec:seds}) reveals significant ongoing star formation
($\textnormal{SFR}>50$~\msun~yr$^{-1}$) in the 14/29 galaxies with
WISE 22~$\mu$m detections, calling into question the post-starburst
nature of roughly half of the HST sample.

Using the F814W filter on the WFC3/UVIS channel, which has
$0.04\arcsec$ pixels, we obtained $4\times10$~min exposures in a
single orbit for each galaxy.  The dithered images were processed with
MultiDrizzle\footnote{http://stsdas.stsci.edu/multidrizzle/} to
produce science mosaics with $0.02\arcsec$ pixels.  For each galaxy,
we use GALFIT \citep{pen02} to model the two-dimensional surface
brightness profile with a single Sersic component (characterized by
Sersic index $n$ and effective radius $r_e$), using stars in the
images to construct the model point-spread function (PSF).  In cases
where the best-fit model returns $n>4$, we also fit an $n=4$ de
Vaucouleurs model, yielding a larger $r_e$ value (due to the
covariance between $n$ and $r_e$), and we use these these larger
effective radii in our analysis.

In this Letter, we highlight the galaxies with the smallest $r_e$ and
largest $\sigmasfr$ values because such extreme starbursts could
conceivably produce the high-velocity outflows we observe (see
Section~\ref{sec:discussion}).  We show HST images for the three
highest $\sigmasfr$ galaxies in Figure~\ref{fig:seds}.  In all three
cases, the single-component GALFIT model accounts for $>85\%$ of the
total flux.  The residuals show diffuse emission that is consistent
with these systems being late-stage galaxy mergers, although we defer
a detailed comparison of the observed morphologies with expectations
from merger simulations to future work.

For the most compact galaxy (J0905+5759, $r_e=0.013\arcsec$ or
100~pc), we also show the observed one-dimensional surface brightness
profile in Figure~\ref{fig:profile}.  We compare to the profiles of
six stars in the same image, the best-fit de Vaucouleurs model, and a
de Vaucouleurs model with $r_e=0.04\arcsec$ (the native WFC3/UVIS
pixel size, which corresponds to a physical scale of 290~pc).  This
comparison illustrates that this galaxy, while only marginally
resolved with an $r_e$ that is $\sim20\%$ of the image FWHM, is
clearly more extended than a point source.

For such a compact source, there is uncertainty in our $r_e$
measurement given uncertainties in the model PSF.  To quantify this,
we used TinyTim to generate a model PSF that is narrower than the
stars in the image (convolving with a $\textnormal{FWHM}=0.04\arcsec$
Gaussian, whereas the image FWHM is $0.074\arcsec$) and found that
this increased the $r_e$ in the GALFIT model by a factor of two.  We
also fit a two-component PSF+Sersic model, but found that the Sersic
component dominates the fit, yielding a similar $r_e$.  Furthermore,
the spectrum of the galaxy shows no evidence for an AGN contribution
to the optical continuum (see Figure~\ref{fig:spectra}), so there is
no clear motivation for including an unresolved, point-source
component in the model.  We conclude that this galaxy is quite compact
and that our $r_e$ estimate is accurate within a factor of two.

\begin{figure}[!t]
\includegraphics[angle=0,scale=0.41]{f2.ps}
\caption{One-dimensional surface brightness profile for J0905+5759,
  which has the smallest effective radius in the sample.  The observed
  profile is shown as the solid black line, and the profiles of six
  stars in the same image are shown in blue, normalized to the same
  central surface brightness.  The best-fit de Vaucouleurs profile
  with $r_e=100$~pc is shown as a dashed red line, and for comparison
  a broader profile with $r_e=0.04\arcsec=290$~pc is shown as the
  dotted green line.  This galaxy is quite compact, but is more
  extended than a point source.}
\label{fig:profile}
\end{figure}

\subsection{Star Formation Rates and Stellar Masses}\label{sec:seds}

% We gathered photometry from the All-Sky Release of the Wide-field
% Infrared Survey Explorer \citep[WISE,][]{wri10}, the Seventh Data
% Release of the Sloan Digital Sky Survey \citep[SDSS,][]{aba09}, and
% General Release 6 from the Galaxy Evolution Explorer
% \citep[GALEX,][]{mar05galex}.  
We gathered photometry from the WISE All-Sky Release, the SDSS Seventh
Data Release, and GALEX General Release 6.  We also obtained
$5\times30$~sec dithered exposures at 3.6~$\mu$m and 4.5~$\mu$m for
all sources with the Infrared Array Camera on the Spitzer Space
Telescope as part of GO program 60145.  We used the post--basic
calibrated data to perform aperture photometry on all sources and
point-source photometry on sources in crowded fields.  We show
spectral energy distributions (SEDs) for the three highest $\sigmasfr$
galaxies in Figure~\ref{fig:seds}.

% All the photometry was corrected for Galactic extinction
% based on the \citet{sch98} dust maps.

We estimate IR-based SFRs for the 25/29 galaxies with WISE 12 or
22~$\mu$m detections by fitting \citet{cha01} templates to their 12
and 22~$\mu$m fluxes.  For the 14/25 galaxies with 22~$\mu$m
detections, this yields SFRs that agree with those obtained from the
\citet{ruj12} method based on 24~$\mu$m luminosity with a scatter of
0.05~dex.  We note that several authors have shown that the shape of
the IR SED for star-forming galaxies depends on $\sigmasfr$
\citep{ruj11,elb11}, with more compact starbursts having larger
total-IR (8--1000~$\mu$m) to mid-IR (8--24~$\mu$m) ratios,
characteristic of the most luminous galaxies in the local universe
\citep{rie09}.  If we used the most luminous local templates for the
8/25 sources with SFRs in the ULIRG regime
($\sfrir>100$~\msun~yr$^{-1}$), we would obtain SFRs that are larger
by 0.5~dex than the values we adopt for this paper.

We also estimate SFRs and stellar masses based on stellar population
fits to the $\lrest=0.1$--3~$\mu$m SEDs using the method of
\citet{mou11}.  For the 14/25 galaxies with
$\sfrir>50$~\msun~yr$^{-1}$, there is agreement between these UV-based
SFR estimates and $\sfrir$ with a scatter of 0.32~dex.  For an SMC
dust law, we find a median attenuation of $A_V=0.4$~mag.  We note that
the observed H$\beta$ luminosities, uncorrected for dust extinction,
are typically factors of 10--$20\times$ smaller than expected from the
UV and IR SFRs.  This can be reconciled by either strong differential
dust attenuation (i.e., $A_V\approx2$--3~mag for the line-emitting
region), escaping ionizing photons from matter-bounded \hii\ regions,
or a recently quenched starburst ($t>5~$Myr) with a small ratio of
ionizing ($\lambda<912$~\AA) to non-ionizing UV photons.

\begin{figure}[!t]
\includegraphics[angle=0,scale=0.41]{f3.ps}
\caption{Spectra covering $\lrest=2500$--5200~\AA\ for the three
  galaxies shown in Figure~\ref{fig:seds}.  For clarity the top two
  spectra are offset by $+10$ and $+20$ units.  These spectra are
  dominated by the light of a young stellar population but have
  relatively weak nebular emission lines (\oii~$\lambda3727$,
  H$\beta$~$\lambda4861$, \oiii~$\lambda5007$) and strong
  \mgii~$\lambda\lambda2796,2803$ absorption arising from the
  interstellar medium.  The absense of broad \mgii\ or H$\beta$
  emission lines rules out a significant contribution to the optical
  continuum light from an AGN.  The panels on the right highlight the
  region around the \mgii\ doublet in both wavelength and velocity
  space to illustrate the outflow kinematics.  The spectrum in the
  bottom panel has sufficient spectral resolution
  ($\textnormal{FWHM}\approx8$~\kms) to resolve the intrinsic shape of
  the absorption-line profile, revealing that the gas near the
  centroid velocity ($v=-2470$~\kms) covers the entire galaxy.}
\label{fig:spectra}
\end{figure}

\begin{figure*}[!t]
\begin{center}
\includegraphics[angle=0,scale=.8]{f4.ps} 
\caption{SFR surface densities and stellar masses for the HST--WISE
  sample described in this paper (black circles, with symbol size
  proportional to outflow velocity), along with samples of $z<0.3$
  gas-rich mergers (orange squares) and $z\sim1$ star-forming galaxies
  (shown with 68\%, 95\%, and 99.7\% contours).  We mark the empirical
  threshold for launching winds \citep[dotted line,
    $\sigmasfr\approx0.1$~\units;][]{hec02}, the 90th-percentile
  starburst intensity limit from \citet{meu97} (dashed line,
  $\sigmasfr\approx25$~\units), and the Eddington limit from radiation
  pressure on dust grains \citep[solid line,
    $\sigmasfr\approx3000$~\units;][]{mur05,tho05,hop10}.  The
  representative error bar in the top-right portion of the plot
  corresponds to uncertainties of 0.3~dex in $\sigmasfr$ and 0.2~dex
  in stellar mass.  Our HST--WISE sample overlaps with the region
  characterized by gas-rich mergers, and extends to very large SFR
  surface densities near the Eddington limit, suggesting growth that
  is limited by momentum injection from massive stars.}
\label{fig:sigmasfr}
\end{center}
\end{figure*}

\subsection{Outflow Kinematics and Covering Factors}

We present $\lrest=2500$--5200~\AA\ spectroscopy for three
high-$\sigmasfr$ sources in Figure~\ref{fig:spectra} based on data
from MMT/Blue Channel and SDSS (J1506+5402), Magellan/MagE
(J1341-0321), and Keck/LRIS and Keck/HIRES (J0905+5759).  The spectra
are dominated by light from a young ($t<50$~Myr) stellar population.
We highlight the interstellar medium \mgii~$\lambda\lambda2796,2803$
absorption lines, which are used to measure outflow velocities.  At
low spectral resolution (e.g., the top right panel of
Figure~\ref{fig:spectra}) it is not possible to determine the
intrinsic shape of the absorption line profile and therefore the
covering factor of the outflowing gas.  However, the Keck/HIRES
spectrum of J0905+5759 ($\textnormal{FWHM}\approx8$~\kms) reveals that
the gas covers the entire continuum source near the velocity centroid
($v=-2470$~\kms) indicating a galaxy-wide outflow.

\section{Discussion}\label{sec:discussion}
